---
title: "Sales and Weather Info Description"
author: Fan E
date: Jun. 10, 2015
output: 
  pdf_document:
    toc: true
    keep_tex: true
    number_sections: true
---

\newpage


# Introduction
The report is a basic description of the original sales and weather data. 

The "units" and "price" columns are aggravated by categories on daily basis. 

## A Sample of Data Table:"sales"

```{r}

head(sales)

```

The total number of observations is `r nrow(sales)` . 

# Statistical Descriptions 

## A brief summary on each column 

```{r}

summary(sales)

```

## Histogram on Temperatures

```{r}

hist(sales$max_temp_amt)
hist(sales$min_temp_amt)
hist(sales$precipitation_mm_amt)
hist(sales$snow_cm_amt)

```

## Histogram on Sales

### Batteries 

```{r}

hist(sales$BATTERIES_QTY)
hist(sales$BATTERIES_PRICE)

```

### Heating and cooling parts

```{r}

hist(sales$HEATING_COOLING_QTY)
hist(sales$HEATING_COOLING_PRICE)

```

### Brakes

```{r}

hist(sales$BRAKES_QTY)
hist(sales$BRAKES_PRICE)

```

### Steering and suspension

```{r}

hist(sales$STEERING_QTY)
hist(sales$STEERING_PRICE)

```

## Skewness Statistics

### Skewness statistics on sales data 

```{r}

apply(sales[, c(10:17)],2,skewness)

```



